### 2016-06-22 appendix.tex
Commit first
Updates on Experiments Graphs

\appendix
\section{Proofs of Theorems}
\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
%\begin{proof}
%Let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
%of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
%all possible valid sequence. It is easy to see that, under such a setting,
%any valid sequence would be captured by one of the partitions in temporal
%replication. This proves the completeness. Now, we compute the minimum value
%of $\eta$ as follows:
%any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
%and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
%as follows:
%\begin{equation}
%\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
%\end{equation}
%With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
%$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
%(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
%validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
%Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
%increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
%observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
%conditions naturally derive
%$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%%with the smallest length. Note that there could be many qualified $T'$s. 
%%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%%If every partition is of at least such a size, then $T'$ must be
%%captured by at least one of the partition. Thus, the pattern $P$ would 
%%be valid in that partition. This proves the completeness.
%\end{proof}

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}

\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
\begin{proof}
Let $B*$ be the assignment matrix wrt the optimal numbering.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, given a numbering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. Moreover,
let $d_i$ denote the degree of vertex $i$, 
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. This is because renumbering the
vertexes does not affect the average degree.
Since $B=\text{triu}(PAP^T)$, entries in $B$ can be written as :
\begin{equation*}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

>>>>

\appendix
\section{Proofs of Theorems}
\subsection{Proof of Theorem~\ref{THM:RP_ETA}} 
\label{appx:proof-rp-eta}
\begin{proof}
We compute $\eta$ by analyzing $\range(\rho_{G,L,K}(\cdot))$.
In the following, when no ambiguity, we use $\rho(T)$ to represent
$\rho_{G,L,K}(T)$. For any sequence $T$, its $\rho(T)$ can
be viewed as interleaving segments and gaps. 
We may view $\rho(T)$ as $l_1,g_1,\ldots, l_{n-1}, g_{n-1}, l_n$, where $l_i$ is a
segment and $g_i$ is a gap. For simplicity, we use $l_i$ and $g_i$ directly as their sizes.
Then the
range of $\rho(T)$ is $\Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i$. 
Since $\rho(T)$ is valid, the following constraints holds: 
(1) $\Sigma_{i=1}^{i=n} l_i \geq K$; (2) $\forall l_i$, $l_i \geq L$;
(3) $\forall g_i$, $g_i \leq G-1$. Based on constraint (1) and (2), 
$n \leq \lceil \frac{K}{L}\rceil$. 
This indicates that $\Sigma_{i=1}^{i=n-1} g_i \leq (\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
If $l_n > L$ and $\Sigma_{i=1}^{i=n} l_i > K$, we can reduce the range of $\rho(T)$
by reducing $l_n$. If $\Sigma_{i=1}^{i=n} l_i - K < l_n - L$ 
then, $\Sigma_{i=1}^{i=n} l_i - K$ can be reduced to $K$. In this case, the maximum range of $\rho(T)$ is 
$\leq K +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
Otherwise, we can reduce $l_n$ to be $L$. When $l_n = L$, 
since we wish $\rho(T)$ to be minimum, it indicates $\Sigma_{i=1}^{i=n} l_i \leq K-1$.
Therefore $\Sigma_{i=1}^{i=n} l_i \leq K-1+L$. In this case,
the maximum range of  $\rho(T)$ is $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$.
Taking maximum, the maximal possible $\rho(T)$ for all $T$s is thus $K-1+L +(\lceil \frac{K}{L}\rceil -1 ) (G-1)$. This proves the first half of the theorem.

For the second half of theorem, we prove by construction. Given $G,L,K$, let $\eta^*$
be the optimal value. Then consider the sequence $T$ generated 
by replicate the following pattern: a $L$-segment followed by $G$-gap. The replication
stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
It is easy to see that the minimum $\range(\rho(T))$ 
is $(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Since $\eta^*$ is optimal,
$\eta^* \geq \range(\rho(T)) = (\lceil \frac{K}{L}\rceil -1 ) (G-1) + K$. Recall $\eta =(\lceil \frac{K}{L}\rceil -1 ) (G-1) + K +L-1$, this implies that $\eta \leq \eta^* + L - 1$. 
\end{proof}
%\subsection{Proof of Theorem~\ref{THM:RP_ETA}}
%\begin{proof}
%Let $T'$ be the \emph{shortest} valid subsequence (wrt. $K,L,G$) 
%of a valid sequence $T$. Let $\eta$ be the upper bound for all $T'$s among 
%all possible valid sequence. It is easy to see that, under such a setting,
%any valid sequence would be captured by one of the partitions in temporal
%replication. This proves the completeness. Now, we compute the minimum value
%of $\eta$ as follows:
%any $T'$ can be viewed as $n$ consecutive segments with sizes $l_1,..,l_n$
%and $n-1$ gaps with sizes $g_1,...,g_{n-1}$. Since $\eta$ is the upper bond among all $T'$s, $\eta$ can be formulated 
%as follows:
%\begin{equation}
%\eta = \max_{n,l_i,g_i} \{ \Sigma_{i=1}^{i=n} l_i + \Sigma_{i=1}^{i=n-1} g_i \}
%\end{equation}
%With the following constraints: (1)$\forall l_i, L \leq l_i \leq K-1$;(2)
%$\forall g_i, 1 \leq g_i \leq G$; (3) $\Sigma_{i=1}^{i=n} l_i \geq K$ and
%(4) $\Sigma_{i=1}^{i=n-1}l_i  \leq K-1$. The constraint (1)(2)(3) due to the 
%validity of $T'$ and the constraint (4) is because of the minimum size of $T'$.
%Observe that, constraints (1)-(4) form a convex polygon and $\eta$ is monotone
%increasing wrt. $n,l_i,g_i$, the maximum value of $\eta$ is thus taken at the boundaries. Further
%observe that $n \in [2, \lceil \frac{K}{L} \rceil]$ and $K \geq 1$, these
%conditions naturally derive
%$\eta = (\lceil \frac{K}{L} \rceil -1)*G+2K -2$.
%%valid pattern $P$, let $T'$ be the subsequence of $P.T$ which conforms to $K,L,G$ 
%%with the smallest length. Note that there could be many qualified $T'$s. 
%%Let the $i^{th}$ local-consecutive segment of $T'$ be $l_i$ and 
%%let the $i^{th}$ gap of $T'$ be $g_i$. Then, the size of $T'$ can 
%%be written as $\Sigma_i (l_i + g_i)$.  Since $T'$ conforms to $K,L,G$, 
%%then $2K \geq \Sigma_i (l_i) \geq K$, $l_i \geq L$, $g_i \leq G$. 
%%It follows: $\Sigma_i(l_i+g_i) \leq (\lceil \frac{K}{L} \rceil -1) *G+2K$. 
%%If every partition is of at least such a size, then $T'$ must be
%%captured by at least one of the partition. Thus, the pattern $P$ would 
%%be valid in that partition. This proves the completeness.
%\end{proof}

%\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT} and Lemma~\ref{LEM:SPM_CORRECT}}

\subsection{Proof of Theorem~\ref{THM:SPM_LB}}
\begin{proof}
We formalize optimization of $\Gamma$ using a linear algebra model as follows:  
Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
A vertex order is in fact a permutation of $J$. Therefore,
the adjacent matrices of any reordered graphs can be represented as $PJP^T$
where $P \in \mathbb{P}$ is a 
\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
$\Gamma^*$ can then be formulated as follows:
\begin{equation}
\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
\end{equation}

Let $B*$ be the assignment matrix wrt the optimal vertex order.
Since we have a star for each object, by the degree-sum formula and pigeon-hole theorem, 
$\Gamma^*=||B^*\vec{b}||_\infty \geq d/2$.
Next, given a numbering $P$, let $e_{i,j}$ be an entry in $PAP^T$. Since 
edges in graph $G$ are independent, then $e_{i,j}$s are independent. Moreover,
let $d_i$ denote the degree of vertex $i$, 
then $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$. This is because renumbering the
vertexes does not affect the average degree.
Since $B=\text{triu}(PAP^T)$, entries in $B$ can be written as :
\begin{equation*}
b_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made. First, since $e_{i,j}$s are independent,
$b_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$s are independent. 
$E[b_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

### 2016-06-22 sec3_definitions.tex
Some revisement
Section 4, Section 5 needs to merge
Checkpoint
Saved algo part
Some updates
On sec4
Need to update \eta
Need to describe \eta
Commit first
Updates on Experiments Graphs

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =\{1,2,...,m\}$ be the descritized temporal dimension. A time sequence $T$ is defined as a subset of $\mathbb{T}$, i.e., $T \subseteq \mathbb{T}$, and we use $|T|$ to denote sequence length. Let $T_i$ be $i$-th entry in $T$ and we say $T$ is consecutive if $\forall 1\leq i\leq |T|-1$, $T_{i+1} = T_i + 1$. It is obvious that any time sequence $T$ can be decomposed into consecutive segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} if the length of all the consecutive segments is no smaller than $L$.

As illustrate in Figure~\ref{fig:platoon_weakpoint}, patterns adapting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from \emph{loose connection} problem. 
To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:
%To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?
%
%
%We say a sequence $T$ is \emph{(fully)consecutive}
%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

%\begin{definition}[$L$-consecutive~\cite{li2015platoon}]
%A time sequence $T$ is $L$-consecutive if each of its consecutive portions 
%has cardinality greater or equal to $L$.
%\end{definition}

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
 $\forall T_i,T_{i+1} \in T, T_{i+1}-T_{i} \leq G$.
\end{definition}

We take $T=\{1,2,3,5,6\}$ as an example, which can be decomposed into two consecutive segments $\{1,2,3\}$ and $\{5,6\}$. $T$ is not $3$-consecutive since the length $\{5,6\}$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. It is worth noting that $T$ is not $1$-connected because the gap between $T_3$ and $T_4$ is 2 (i.e., 5-3=2).

%Given a timestamp $t$, objects with their locations at $t$ collectively form a \emph{snapshot}\footnote{Missing time stamps can be interpreted using existing methods such as linear interpolation~\cite{jeung2008convoy}.}.Objects in a snapshot can then be clustered based on the closeness of their locations. Let $C_t(o_i)$ be the cluster which $o_i$ belongs to at time $t$, a general co-movement pattern can be defined as:
Given a trajectory database descritized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.

%\begin{enumerate}
%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
%\item{Significance: $|O| \geq M$}
%\item{Duration: $|T| \geq K$}
%\item{Consecutiveness: $T$ is $L$-consecutive}
%\item{Separateness: $T$ is $G$-separated}
%\end{enumerate} 
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. By customizing these parameters, our pattern can 
express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
%In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. 
%
%As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent. By setting appropriate $G$, we are able to prune this anomaly. 
It is notable that GCMP cannot be modeled by existing patterns. AS MENTIONED IN WECHAT, POLISH THIS PART.

%The general co-movement pattern retains the patterns that discovered by all 
%existing techniques (group, flock, convoy, swarm and platoon). 
%The relationships between general co-movement pattern and other patterns are summarized 
\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
Pattern & $M$ & $K$ & $L$ & $G$ & Clustering\\ 
\hline
Group & $2$ & $1$ & $2$ & $|T|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|T|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|T|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicate a user specified value. $M$ represents the 
object \emph{size} constraints. $K$ represents \emph{duration} constraint. $L$ represents \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraints.}
\label{tbl:patterns}
\end{table}

It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:
%
%To reduce the size of output, 
%we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern.

@@

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact. 
%LETS KEEP THE CLOSED INFORMATION AT THE MOMENT. IF NO CLOSED IS DEFINED, WE CANNOT REDUCE GCMP TO OTHER PATTERNS SINCE THOSE PATTERNS ARE ALL DEFINED AS ``CLOSED''
%For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_3,o_4\} \{1,2,3\}$ in Figure~\ref{fig:related_work} is not a closed pattern, while $\{o_3, o_4\} \{t_1,t_2,t_3\}$ is a closed pattern.

%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes. Therefore in this paper, we mainly consider density-based clustering.
Our definition of GCMP is free from clustering method. Users are able to supply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the user.

In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory data.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
Symbols & Meanings \\
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline
$M$ & Object size constraint \\
\hline 
$K$ & Duration constraint\\
\hline
$L$ & Consecutiveness constraint\\
\hline
$G$ & Connection constraint \\
\hline
$T$ & Time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

>>>>

\section{Definitions}
\label{sec:definition}
Let $\mathbb{O} = \{o_1 ,o_2,...,o_n\}$ be the set of objects and $\mathbb{T} =(1,2,...,m)$ be the discretized temporal dimension. 
A time sequence $T$ is defined as a ordered subset of $\mathbb{T}$. 
Let $T[i]$ be the $i$-th entry of the sequence $T$ and $i$ starts from 1.
We allow the traditional set operators 
such as \emph{membership}, \emph{union}, \emph{intersect},
\emph{difference}, \emph{candinality}, \emph{min},  \emph{max} and  \emph{range} on 
sequences without changing their semantics. 
Since sequences are ordered, we distinguish the concept of \emph{subset}
and \emph{subsequence}. Given two sequence $T_1$ and $T_2$, 
$T_1$ is a \emph{subset} of $T_2$, if $\forall t \in T_1$ implies $t \in T_2$.
$T_1$ is a \emph{subsequence} of $T_2$, if $\exists i \in (0,..,|T_2|), \forall j \in (1,..,|T_1|),  T_1[j]=T_2[i+j]$.
It is notable that a subsequence is always a subset, but not vice versa. We use $T[i:j]$ to denote
the subsequence of $T$ from $i$-th entry to $j$-th entry inclusively.

We say a sequence $T$ is consecutive 
if $\forall i \in (1,...,|T|-1), T[i+1] = T[i] + 1$.  We refer a consecutive
portion of $T$ as a \emph{segment}.
It is obvious that any time sequence $T$ can be decomposed into
segments and we say $T$ is \textit{L-consecutive}~\cite{li2015platoon} 
if the length of every segment is no smaller than $L$.

As illustrated in Figure~\ref{fig:platoon_weakpoint}, patterns adopting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from the \emph{loose connection} problem. 
To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
 $\forall i \in (1,...,|T|-1), T[i+1]-T[i] \leq G$.
\end{definition}

We take $T=(1,2,3,5,6)$ as an example, which can be decomposed into two segments $(1,2,3)$ and $(5,6)$. $T$ is not $3$-consecutive since the length of $(5,6)$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. It is worth noting that $T$ is not $1$-connected because the gap between $T[3]$ and $T[4]$ is 2 (i.e., 5-3=2).

Given a trajectory database discretized into snapshots, we can conduct a clustering method, either disk-based or density-based, to identify groups with spatial proximity. Let $T$ be the set of timestamps in which a group of objects $O$ are clustered. We are ready to define a more general co-movement pattern:
\begin{definition}[General Co-Movement Pattern]
A general co-movement pattern finds a set of objects $O$ satisfying the following five constraints: 1) \textit{closeness:} the objects in $O$ belong to the same cluster in the timestamps of $T$; 2) \textit{significance:} $|O| \geq M$; 3) \textit{duration:} $|T| \geq K$; 4) \textit{consecutiveness:} $T$ is L-consecutive; and 5) \textit{connection:} $T$ is $G$-connected.
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$.  By customizing these parameters, our pattern can 
express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|\mathbb{T}|$, we achieve the \emph{platoon} pattern. By setting $G=|\mathbb{T}|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|\mathbb{T}|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} patterns. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
It is notable that GCMP cannot be modeled by existing patterns. 
\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
Pattern & $M$ & $K$ & $L$ & $G$ & Clustering\\ 
\hline
Group & $2$ & $1$ & $2$ & $|\mathbb{T}|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|\mathbb{T}|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|\mathbb{T}|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicates a user specified value. $M$ represents the 
object \emph{size} constraint. $K$ represents the \emph{duration} constraint. $L$ represents the \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraint.}
\label{tbl:patterns}
\end{table}

It is also observable that the number of patterns in GCMP could be exponential under some parameter settings (i.e., 
when expressing \emph{swarm}). In particular, given a parameter $M$, if a pattern $P$ is valid, then any subset of $P$ with 
size $M$ is also a valid pattern. This results in additional $\Sigma_{M\geq i \geq |P.O|} {|P.O| \choose i}$ patterns,
which is clearly overwhelming and redundant. For all these patterns, output $P$ is sufficient. Therefore, we define the \emph{Closed General Co-Movement Pattern} as follows:

@@

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern since $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.

Our definition of GCMP is independent of the clustering method. Users can apply different clustering methods to facilitate different application needs. 
We currently expose both disc-region based clustering and DBSCAN as options to the users.

In summary, the goal of this paper is to present a parallel solution for discovering closed GCMP from large-scale trajectory datasets.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
Symbols & Meanings \\
\hline
$S_t$ & snapshot of objects at time $t$ \\
\hline
$M$ & object size constraint \\
\hline 
$K$ & duration constraint\\
\hline
$L$ & consecutiveness constraint\\
\hline
$G$ & connection constraint \\
\hline
$P=(O:T)$ & pattern with object set $O$, time sequence $T$\\
\hline
$\eta$ & replication factor in TRM\\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$S_t$ & the set of clusters at time $t$\\
\hline 
$\lambda_i$ & the partition with snapshots $S_t,..,S_{t+\eta-1}$ \\
\hline
$Sr_i $ &  the star of object $i$ \\
\hline 
\end{tabular} 
\caption{Symbols and notions used}
\end{table}
